Finite Complete Suites for CSP Refinement Testing

### 2019-04-17 scp-journal/article-revision-1/main.tex
Small changes due to remarks from Wen-ling. READY FOR RE-SUBMISSION

The branches of an external choice can be protected by guards. The process
$$
P(x_1,\dots,x_n) = \text{bexpr}_1(x1,\dots,x_n) \& Q(x_1,\dots,x_n) \extchoice
\text{bexpr}_2(x1,\dots,x_n) \& R(x_1,\dots,x_n)
$$
parametrised over $x_1,\dots,x_n$ branches according to Boolean expressions
$\text{bexpr}_1(x1,\dots,x_n)$ and $\text{bexpr}_2(x1,\dots,x_n)$ over
variables from $\{ x_1,\dots,x_n\}$: if $\text{bexpr}_1(x1,\dots,x_n)$ evaluates to
$\ist$ and $\text{bexpr}_2(x1,\dots,x_n)$ to $\isf$, $P$ behaves like $Q$.
If $\text{bexpr}_1(x1,\dots,x_n)$ evaluates to
$\isf$ and $\text{bexpr}_2(x1,\dots,x_n)$ to $\ist$, $P$ behaves like $R$. If both
Boolean expressions evaluate to $\ist$, $P$ behaves as $Q\extchoice R$. Finally, if
both Boolean expressions evaluate to $\isf$, $P$ behaves like $\Stop$.

@@

It is assumed that the events $\efail$ and $\epass$, indicating verdicts FAIL
and PASS for the test execution, are not included in $\Sigma$. Since we
assume that $Q$ is free of livelocks, the events $\efail$ or $\epass$ always
become visible, if they are the only events $U_F(j)/s$ is ready to engage in:
if $U_F(j)/s$ can only produce $\epass$ or $\efail$, the occurrence of these
events can never be blocked due to a livelock, since the only
  process executing concurrently with  $U_F(j)$  is livelock-free  $Q$.

>>>>

The branches of an external choice can be protected by guards. The process
$$
P(x_1,\dots,x_n) = \text{bexpr}_1(x_1,\dots,x_n) \& Q(x_1,\dots,x_n) \extchoice
\text{bexpr}_2(x_1,\dots,x_n) \& R(x_1,\dots,x_n)
$$
parametrised over $x_1,\dots,x_n$ branches according to Boolean expressions
$\text{bexpr}_1(x_1,\dots,x_n)$ and $\text{bexpr}_2(x_1,\dots,x_n)$ over
variables from $\{ x_1,\dots,x_n\}$: if $\text{bexpr}_1(x_1,\dots,x_n)$ evaluates to
$\ist$ and $\text{bexpr}_2(x_1,\dots,x_n)$ to $\isf$, $P$ behaves like $Q$.
If $\text{bexpr}_1(x_1,\dots,x_n)$ evaluates to
$\isf$ and $\text{bexpr}_2(x_1,\dots,x_n)$ to $\ist$, $P$ behaves like $R$. If both
Boolean expressions evaluate to $\ist$, $P$ behaves as $Q\extchoice R$. Finally, if
both Boolean expressions evaluate to $\isf$, $P$ behaves like $\Stop$.

@@

It is assumed that the events $\efail$ and $\epass$, indicating verdicts FAIL
and PASS for the test execution, are not included in $\Sigma$. Since we
assume that $Q$ is free of livelocks, the events $\efail$ or $\epass$ always
become visible, if they are the only events that $U_F(j)/s$ is ready to engage in:
if $U_F(j)/s$ can only produce $\epass$ or $\efail$, the occurrence of these
events can never be blocked due to a livelock, since the only
  process executing concurrently with  $U_F(j)$  is livelock-free~$Q$.
